---
title: "Publishing Instructions"
author: "Emily Smenderovac"
date: "3/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(blogdown)
```

## Website Basis

The website skeleton is adapted from the wowchemy academic-starter theme. Which can be downloaded below.

```{r create_site, eval=FALSE}
## Make sure you have most recent version of hugo installed

blogdown::new_site(theme = "wowchemy/starter-academic", sample=TRUE)

```

Initial example site used as basis, then modifications made to css, js and html to allow for pages to be made in the required ways.

## Make sure you have most recent version of hugo installed

```{r update_hugo}
blogdown::hugo_version()
## if you don't have the newest, update
blogdown::install_hugo()
## update options for new version
options(blogdown.hugo.version = "0.82.0")

```

## Updating and Adding content

Two helper scripts have been written to help make the periodic updating of website content easier. These are located in the website_content_creation folder, along with folders containing images and author form submissions. 


## Build the website for hosting on github

```{r publish}
blogdown::hugo_build(local=FALSE, relativeURLs = TRUE)
```

After building the site with hugo, rename the public folder to 'docs'.


**Caution: Make sure to delete and replace the docs folder when re-publishing to ensure all content is overwritten!**


## Publish to web

On github, go to the pages section of the settings for the website repository. Select the docs folder as the folder to publish from. After this, updating the git repository after publishing and renaming the docs folder will update the website.


