---
title: "Publishing Instructions"
author: "Emily Smenderovac"
date: "3/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(blogdown)
```

## Website Basis

The website skeleton is adapted from the wowchemy academic-starter theme. Which can be downloaded below.

```{r update_hugo}
## Make sure you have most recent version of hugo installed

blogdown::new_site(theme = "wowchemy/starter-academic", sample=TRUE)

```

Initial example site used as basis, then modifications made to css, js and html to allow for pages to be made in the required ways.

## Make sure you have most recent version of hugo installed

```{r update_hugo}
blogdown::hugo_version()
## if you don't have the newest, update
blogdown::install_hugo()
## update options for new version
options(blogdown.hugo.version = "0.82.0")

```

## Create a version of the website for the web


```{r publish}
blogdown::hugo_build(local=FALSE, relativeURLs = TRUE)
```

## Publish to web

On github, go to the pages section of the options on the website repository. Select the public folder as the folder to publish from. After this, updating the git repository after publishing will update the website.

Caution: Make sure to delete and replace the public folder when re-publishing to ensure all content is overwritten!
